% --- Template for thesis / report with tktltiki2 class ---
% 
% last updated 2013/02/15 for tkltiki2 v1.02

\documentclass[finnish]{tktltiki2}

% tktltiki2 automatically loads babel, so you can simply
% give the language parameter (e.g. finnish, swedish, english, british) as
% a parameter for the class: \documentclass[finnish]{tktltiki2}.
% The information on title and abstract is generated automatically depending on
% the language, see below if you need to change any of these manually.
% 
% Class options:
% - grading                 -- Print labels for grading information on the front page.
% - disablelastpagecounter  -- Disables the automatic generation of page number information
%                              in the abstract. See also \numberofpagesinformation{} command below.
%
% The class also respects the following options of article class:
%   10pt, 11pt, 12pt, final, draft, oneside, twoside,
%   openright, openany, onecolumn, twocolumn, leqno, fleqn
%
% The default font size is 11pt. The paper size used is A4, other sizes are not supported.
%
% rubber: module pdftex

% --- General packages ---

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsfonts,amsmath,amssymb,amsthm,booktabs,color,enumitem,graphicx}
%\usepackage[pdflatex,hidelinks]{hyperref}
\usepackage[hidelinks]{hyperref}


% Automatically set the PDF metadata fields
\makeatletter
\AtBeginDocument{\hypersetup{pdftitle = {\@title}, pdfauthor = {\@author}}}
\makeatother

% --- Language-related settings ---
%
% these should be modified according to your language

% babelbib for non-english bibliography using bibtex
\usepackage[fixlanguage]{babelbib}
\selectbiblanguage{finnish}

% add bibliography to the table of contents
\usepackage[nottoc]{tocbibind}
% tocbibind renames the bibliography, use the following to change it back
\settocbibname{Lähteet}

% --- Theorem environment definitions ---

\newtheorem{lau}{Lause}
\newtheorem{lem}[lau]{Lemma}
\newtheorem{kor}[lau]{Korollaari}

\theoremstyle{definition}
\newtheorem{maar}[lau]{Määritelmä}
\newtheorem{ong}{Ongelma}
\newtheorem{alg}[lau]{Algoritmi}
\newtheorem{esim}[lau]{Esimerkki}

\theoremstyle{remark}
\newtheorem*{huom}{Huomautus}


% --- tktltiki2 options ---
%
% The following commands define the information used to generate title and
% abstract pages. The following entries should be always specified:

\title{Käyttäytymisen muokkaaminen mobiilisovelluksilla}
\author{Topias Heinonen}
\date{\today}
\level{Aine}
\abstract{Ihmiset tekevät usein itselleen ja yhteiskunnalle parempia valintoja, kun heille antaa enemmän tietoa tai motivaatiota.
Tässä kirjoituksessa käyn läpi tutkimusta mobiilisovelluksista, joiden tarkoituksena on antaa sekä tietoa että motivaatiota parempien valintojen tueksi.
Yksi suosituista tekniikoista tämän saavuttamiseksi on pelillisten elementtien tuominen sovellukseen.
}

% The following can be used to specify keywords and classification of the paper:

\keywords{avainsana 1, avainsana 2, avainsana 3}

% classification according to ACM Computing Classification System (http://www.acm.org/about/class/)
% This is probably mostly relevant for computer scientists
% uncomment the following; contents of \classification will be printed under the abstract with a title
% "ACM Computing Classification System (CCS):"
% \classification{}

% If the automatic page number counting is not working as desired in your case,
% uncomment the following to manually set the number of pages displayed in the abstract page:
%
% \numberofpagesinformation{16 sivua + 10 sivua liitteissä}
%
% If you are not a computer scientist, you will want to uncomment the following by hand and specify
% your department, faculty and subject by hand:
%
% \faculty{Matemaattis-luonnontieteellinen}
% \department{Tietojenkäsittelytieteen laitos}
% \subject{Tietojenkäsittelytiede}
%
% If you are not from the University of Helsinki, then you will most likely want to set these also:
%
% \university{Helsingin Yliopisto}
% \universitylong{HELSINGIN YLIOPISTO --- HELSINGFORS UNIVERSITET --- UNIVERSITY OF HELSINKI} % displayed on the top of the abstract page
% \city{Helsinki}
%


\begin{document}

% --- Front matter ---

\frontmatter      % roman page numbering for front matter

\maketitle        % title page
\makeabstract     % abstract page

\tableofcontents  % table of contents

% --- Main matter ---

\mainmatter       % clear page, start arabic page numbering

\section{Johdanto}

Jokapaikan tietotekniikka (Pervasive Computing) määriteltiin vuonna 1991 tarkoittamaan ympäristöä, jossa tietotekniikka on niin nivoutunut arkeen, että se on muuttunut lähes näkymättömäksi \cite{weiser}.
Käyttäjän ei tarvitse tehtävää tehdessään ajatella käyttämäänsä laitetta, vaan hän voi keskittyä itse tehtävään. Laitteisto reagoi ennakoivasti muutoksiin käyttäjän tilassa ilman suoria komentoja \cite{pervasive}.
Matkapuhelimet ovat houkutteleva alusta jokapaikan tietoteknisille ratkaisuille, sillä ne ovat pieniä, kulkevat mukana jatkuvasti ja sisältävät nykyään tarpeeksi sensoreita monipuoliseen ympäristön havainnointiin.

Vakuuttava teknologia (\cite{weiser})

Esimerkiksi Dance Dance revolution tai Ingress osuvat tämän kirjoituksen ulkopuolelle. Ne lisäävät käyttäjänsä fyysistä aktiivisuutta, mutta niiden tarkoituksena ei ole motivoida liikkumaan, vaan viihdyttää.

Mobiilisovellusten käyttämistä ihmisten käyttäytymisen muokkaamiseen on tutkittu paljon~\cite{houston, ubifit, ubigreen, obesity, movipill, tripzoom}.
Jonkun verran on myös tutkittu olemassaolevia sovelluksia~\cite{fitocracy}.
Hyödyllisiä taustalähteitäkin on~\cite{pervasive,saha2003pervasive,fogg2003persuasive, oinas2009persuasive, fogg1998persuasive}.

\section{Matkantekoon vaikuttavat sovellukset}

Tässä kohdassa käsittelen mobiilisovelluksia, joiden tarkoituksena on vaikuttaa käyttäjän matkantekoon. Näitä ovat UbiGreen~\cite{ubigreen} ja tripzoom~\cite{tripzoom}.

\section{Liikuntaan vaikuttavat sovellukset}

Tässä kohdassa käsittelen mobiilisovelluksia, joiden tarkoituksena on korottaa käyttäjän fyysistä aktiivisuutta. Näitä ovat Houston~\cite{houston}, UbiFit Garden~\cite{ubifit} ja Fitocracy~\cite{fitocracy}. Lisäksi käsittelen Arteaga et al. tutkimusta iPhone-peleistä.

\section{Pelillistäminen}

Käsittelen Pelillistämistä~\cite{gamification} omana kohtanaan. Käsittelen tässä kohdassa myös lääkkeiden ottamiseen kannustavaa MoviPill-peliä. Sen jälkeen tunnistan pelillisiä elementtejä myös aiemmin esittelemistäni sovelluksista.

\section{Yhteenveto}

% --- References ---
%
% bibtex is used to generate the bibliography. The babplain style
% will generate numeric references (e.g. [1]) appropriate for theoretical
% computer science. If you need alphanumeric references (e.g [Tur90]), use
%
% \bibliographystyle{babalpha-lf}
%
% instead.

\bibliographystyle{babalpha-lf}
\bibliography{references-fi}


% --- Appendices ---

% uncomment the following

% \newpage
% \appendix
% 
% \section{Esimerkkiliite}

\end{document}
